Compositional equivalences based on Open pNets

### 2021-10-13 2016-Weak-FH-Bisim/WeakBisim.tex
t_i to solve problem

Consequently, $t_i^{i\in I}$ defines first $I$ the set over which the
family is indexed, and then $t_i$ the elements of the family.
For example $t^{i\in\{3\}}$ is
the mapping with a single entry $t$ at index $3$; exceptionally, for mappings with
only a few entries we use the notation $(3\mapsto t)$ instead.
In this article, sentences of the form ``there exists $t_i^{i\in I}$'' means there exists $I$ and a function that maps each element of $I$ to a term $t_i$.
%The operation  $A[j \mapsto a]$ updates the value associated to $j$ in map $A$ so that 
%it 
%now corresponds to $a$.

>>>>

Consequently, $t_i^{i\in I}$ defines first $I$ the set over which the
family is indexed, and then $t_i$ the elements of the family.
For example $t_i^{i\in\{3\}}$ is
the mapping with a single entry $t_3$ at index $3$; exceptionally, for mappings with
only a few entries we use the notation $(3\mapsto t_3)$ instead.
In this article, sentences of the form ``there exists $t_i^{i\in I}$'' means there exists $I$ and a function that maps each element of $I$ to a term $t_i$.
%The operation  $A[j \mapsto a]$ updates the value associated to $j$ in map $A$ so that 
%it 
%now corresponds to $a$.
